---
title: "AmyPC"
output: pdf_document
---

Volumetrically corrected
reduced 

```{r}

library(readxl)
library(dplyr)
library("devtools")
library("corrplot")
library("ggplot2")
library("survival")
library("Formula")
library("lattice")
library("magrittr")
library("ggpubr")
library("plyr")
library("dplyr")
library("Matrix")
library("lme4")
library("factoextra")
library("ggfortify")
library("Hmisc")
library("tidyr")
library("lme4")
library("lmtest")
library("lmerTest")
library("emmeans")
library("car")
library("cNORM")
library("BBmisc")
library("psych")

```

```{r}
AmyPC <- read_excel("~/Desktop/R/PretermControl/volumetry/CorrectedAmy_PC.xlsx")
str(AmyPC)

AmyPC$Group <- as.factor(AmyPC$Group)

AmyPC$Gender <- as.factor(AmyPC$Gender)

AmyPC$Age <- as.numeric(AmyPC$Age)

AmyPC$Status <- as.factor(AmyPC$Status)

AmyPC$GA <- as.numeric(AmyPC$GA)

AmyPC$Pds_N <- as.numeric(AmyPC$Pds_N)

str(AmyPC)

#check the data for outliers
summary(AmyPC)

levels(AmyPC$Group)

#relevel

AmyPC$Status <- relevel(AmyPC$Status, ref= "Preterm")

```

```{r}

#some overall summaries

library(arsenal)

#writecsv with this table

#Again with Volumetrically Corrected Data


table_one <- tableby(Group ~ ., data= AmyPC)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

tab2

write.csv(tab2, "~/Desktop/AmyPCSummary.csv")



```

To Volumetrically Correct the Data

```{r}

for (column.name in names(AmyPC) [10:ncol(AmyPC)]) {
  AmyPC[column.name] = AmyPC[column.name] / AmyPC$ICV
}

AmyPC

```
#VOLUMETRIC CORRECTIONS


for (column.name in names(AmyPC) [10:ncol(AmyPC)]) {
  AmyPC[column.name] = AmyPC[column.name] / AmyPC$ICV
}

#ANCOVA 

storage <- list()
gavtable <- list()
for(i in names(AmyPC)[-c(1:9)]) {
  storage[[i]] <- AmyPC %>% anova_test(as.formula(paste(i, "~ ICV + Status")))
  gavtable[[i]] <- get_anova_table(storage[[i]])
}

gavtable

View(gavtable)



res.aov <- AmyPC %>% anova_test(left_Lateral_nucleus ~ ICV + Status)
get_anova_table(res.aov)




```{r}
#testing lmer
library(lme4)

l1 <- lm(data= AmyPC, left_Lateral_nucleus~ Status + Age + Pds_N + GA)

summary(l1)

#looping lm for entire data set

storage <- list()
for(i in names(AmyPC)[-c(1:9)]){
  storage[[i]] <- lm(get(i) ~ Status, AmyPC)
}


library(dplyr)
library(tidyr)
library(tidyverse)
library(devtools)


table <-  storage %>% tibble(
    dvsub = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

tab <- as.data.frame(table)

tab

to <- subset(tab, select = -c(2))

head(to)

newtable <- filter(to, term == "StatusControl")

newtable

write.csv(to, "~/Documents/AmyPCpvalues.csv")

head(newtable)

```
Amy <-as.data.frame(AmyPC[,c(9:28)])
dim(Amy)
for (i in 9:length(Amy)) { 
  variable <- Amy[,i]
  lme_cer <- lmer(variable ~ Group + ICV + (1 | Subject), data = AmyPC, REML = FALSE)
print(summary(lme_cer))
}
```{r}


ordered <- newtable[order(newtable$p.value), ]

head(ordered)

write.csv(ordered, "~/Documents/AmyPCorderedpvalues.csv")

pvals <- ordered$p.value

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Documents/correctionsAmypoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(res2, "~/Documents/finalAmypoPCt.csv")


```


```{r}

AmyPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/CorrectedAmy_PC.xlsx")

responseList <- names(AmyPC3)[-c(1:9)]

pwc1 <- list()
for (i in responseList) 
  pwc1[[i]] <- AmyPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Status")), covariate = "ICV",
    p.adjust.method = "fdr")


ph <-data.table::rbindlist(pwc1, fill = T)

ph

#lets just try

ordered <-ph[order(ph$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsAmyPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

```



```{r}

library(emmeans)
library(rstatix)

ThalPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/CorrectedAmy_PC.xlsx")
ThalPC3

responseList <- names(ThalPC3)[-c(1:9)]

pwc1 <- list()
for (i in responseList) 
  pwc1[[i]] <- ThalPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Status")), covariate = "ICV",
    p.adjust.method = "fdr")


ph <-data.table::rbindlist(pwc1, fill = T)

ph
means <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalPCmeans.csv")

filmean <- trymean[-c(1:3), ]

colnames(filmean) <- c("Mean_Preterm", "Mean_Control")

sd <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/HipAsymPCSD.csv")

filsd <- trsd[-c(1:3), ]

colnames(filsd) <- c("SD_Preterm", "SD_Control")

filsd$SD_Post <- as.numeric(filsd$SD_Preterm)


filmean$Mean_Preterm <- paste(filmean$Mean_Preterm, filsd$SD_Preterm, sep=" ±")

filmean$Mean_Control <- paste(filmean$Mean_Control, filsd$SD_Control, sep=" ±")

filmean

colnames(filmean) <- c("Mean ± SD Control", "Mean ± SD Preterm")

filmean

write.csv(filmean, "~/Desktop/PVAL/filtered/ThalMeansSD.csv")


#lets just try

library(effectsize)


stor <- list()
stor2 <- list()
for(i in names(ThalPC3)[-c(1:9)]) {
 stor[[i]] <- aov(as.formula(paste(i, "~ Status")), covariate = "ICV", data= ThalPC3) 
 stor2[[i]] <- effectsize(stor[[i]])
}

ees <-data.table::rbindlist(stor2, fill = T)

ees

phh <- cbind(filmean, ph, ees)

phh

##


ordered <-phh[order(phh$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/hippoASymFINAL.csv")

```







```
