---
title: "HippoPrePost_April7"
output: pdf_document
---



```{r}

library(readxl)
library(dplyr)
library("devtools")
library("corrplot")
library("ggplot2")
library("survival")
library("Formula")
library("lattice")
library("magrittr")
library("ggpubr")
library("plyr")
library("dplyr")
library("Matrix")
library("lme4")
library("factoextra")
library("ggfortify")
library("Hmisc")
library("tidyr")
library("lme4")
library("lmtest")
library("lmerTest")
library("emmeans")
library("car")
library("cNORM")
library("BBmisc")
library("psych")

```

```{r}
HippocampusPrePost <- read_excel("~/Desktop/R/PrePost/Regular/HippocampusPrePost.xlsx")
HippoPrePost <- HippocampusPrePost

str(HippoPrePost)

HippoPrePost$Group <- as.factor(HippoPrePost$Group)

HippoPrePost$Gender <- as.factor(HippoPrePost$Gender)

HippoPrePost$Age <- as.numeric(HippoPrePost$Age)

str(HippoPrePost)

#check the data for outliers
summary(HippoPrePost)

levels(HippoPrePost$Group)

#relevel

HippoPrePost$Group <- relevel(HippoPrePost$Group, ref= "Pre")

```

```{r}

#some overall summaries

library(arsenal)

#writecsv with this table

#Again with Volumetrically Corrected Data


table_one <- tableby(Group ~ ., data= HippoPrePost)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

tab2

write.csv(tab2, "~/Desktop/TableOne/HippoPrePostSummary.csv")





```

To Volumetrically Correct the Data

for (column.name in names(HippoPrePost) [9:ncol(HippoPrePost)]) {
  HippoPrePost[column.name] = HippoPrePost[column.name] / HippoPrePost$ICV
}

view(HippoPrePost)


```{r}
#means 

means <- HippoPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/HippoPrePostmeans.csv")

filmean <- trymean[-c(1:5), ]

filmean

colnames(filmean) <- c("Mean Pre", "Mean Post")

sd <- HippoPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/HipASD.csv")

filsd <- trsd[-c(1:5), ]

colnames(filsd) <- c("SD_Pre", "SD_Post")

filsd$SD_Post <- as.numeric(filsd$SD_Post)

filmean$SD_Pre <- filsd$SD_Pre

filmean$SD_Post <- filsd$SD_Post

filmean

```

#cohen's d

library(rstatix)

dnames <- names(HippoPrePost)[-c(1:7)]

cod <- for(i in seq_along(dnames)){
HippoPrePost %>% cohens_d(left_CA1_body ~ Group, mu = 0, paired= TRUE)

cod

  library(pwr)
cohen.ES(test = 'f2', size = 'large')
```{r}


#volumetrically correcting the data

for (column.name in names(HippoPrePost) [9:ncol(HippoPrePost)]) {
  HippoPrePost[column.name] = HippoPrePost[column.name] / HippoPrePost$ICV
}
  
HippoPrePost


```

```{r}

#testing lmer
library(lme4)

model <- lmer(right_Hippocampal_tail ~ Group + (1 | Subject), data = HippoPrePost, REML = FALSE)

summary(model)


##tring to do a paired sample t.test


library(dplyr)


#visualize data using boxplots

library("PairedData")

# Subset vol data before treatment
before <- subset(HippoPrePost,  Group == "Pre", left_CA3_head,
                 drop = TRUE)
# subset weight data after treatment
after <- subset(HippoPrePost,  Group == "Post", left_CA3_head,
                 drop = TRUE)

# Plot paired data
library(PairedData)
pd <- paired(before, after)
plot(pd, type = "profile") + theme_bw()

ggplot(data=HippoPrePost) + aes(x= Group, y= left_CA3_head, colour= Group) + geom_boxplot()


##checking normality 

# compute the difference
d <- with(HippoPrePost, 
        left_CA3_head[Group == "Pre"] - left_CA3_head[Group == "Post"])
d

# Shapiro-Wilk normality test for the differences
shapiro.test(d) # => p-value = 0.4

#pvalue above 0.05 means that we can assume normality

qqplot <- qqnorm(HippoPrePost$left_CA3_head, pch = 1, frame = FALSE)

histogram(HippoPrePost$left_CA3_head)

#nowt.test (if we were to assume normality) #cant use here since we havent volumetrically corrected the data and need to add it as covariate

res <- t.test(left_CA3_head ~ Group, HippoPrePost, paired = TRUE)
summary(res)

#lmer results

summary(model)

##plot the data

ggplot(HippoPrePost) + aes(x= Group, y = right_Whole_hippocampal_head, color= Group) + geom_boxplot() + labs(title= "Volume of Left CA3_body Pre and Post Mindfulness Intervention", x= "Intervention Group", y= "Volume") 


##Now we use the final lmer formula

fit.compact = lmer(formula = left_CA3_head ~ Group + Age + Gender + (1 | Subject),
                   data = HippoPrePost)
fit.augmented = lmer(formula = left_CA3_head ~ Group + Pds_N + (1 | Subject),
                     data = HippoPrePost)

# compare via Chisq-test
anova(fit.compact, fit.augmented)
```
Hippo <-as.data.frame(HippoPrePost[,c(9:28)])
dim(Hippo)
for (i in 9:length(Hippo)) { 
  variable <- Hippo[,i]
  lme_cer <- lmer(variable ~ Group + ICV + (1 | Subject), data = HippoPrePost, REML = FALSE)
print(summary(lme_cer))
}
```{r}

library(dplyr)
library(tidyr)
library(tidyverse)
library(devtools)
library(broom.mixed)
library(lmerTest)

storage <- list()
for(i in names(HippoPrePost)[-c(1:8)]){
  storage[[i]] <- lmer(get(i) ~ Group + (1 | Subject), data= HippoPrePost, REML = FALSE)
}

library(lme4)
library(broom)
library(broomExtra)

table <-  storage %>% tibble(
    dvsub = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

tab <- as.data.frame(table)

write.csv(to, "~/Desktop/PVAL/ALL/Hippoprepostpvalues.csv")


to <- subset(tab, select = -c(2))


newtable <- filter(to, term == "GroupPost")

newtable


newtable2 <- cbind(filmean, newtable)

newtable2

write.csv(to, "~/Desktop/PVAL/filtered/Hippoprepostpvalues.csv")


write.csv(to, "~/Desktop/PVAL/HippoPrePostMeanSD.csv")

```

```{r}

pvaluec <- subset(newtable, p.value < 0.05)

pvaluec

write.csv(pvaluec, "~/Desktop/pvalues/hippoprepostsigpvalues.csv")

ordered <- newtable2[order(newtable$p.value), ]
ordered

write.csv(ordered, "~/Documents/Hipprepostorderedpvalues.csv")

pvals <- ordered$p.value

```

```{r}

#corrections

FDR = p.adjust(pvals, "fdr")

res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionshippoPrePost.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/finalhippoprepost.csv")

```

```{r}

#graphs of sig regions

fdrsig <- subset(ordered, FDR < 0.1)

fdrsig

nm <- fdrsig$dvsub

nm


for(i in seq_along(nm)) {
plt<- ggplot(HippoPrePost, aes_string(x= "Group", y = nm[i], color= "Group")) + geom_boxplot() + theme_classic() + labs(x= "Group", y= "Volume", title= paste("Volume of ", nm[i], " Pre and Post Mindfulness Intervention", sep = "") )
print(plt)
ggsave(plt, filename = paste("Sig Pre vs Post volume of ", nm[i], ".jpg", sep=""))
Sys.sleep(2)
}

```

```{r}
#there are none in this case but we can run it again for all graphs

colNames <- names(HippoPrePost)[-c(1:7)]

for(i in seq_along(colNames)) {
plt<- ggplot(HippoPrePost, aes_string(x= "Group", y = colNames[i], color= "Group")) + geom_boxplot() + theme_classic() + labs(x= "Group", y= "Volume", title= paste("Volume of ", colNames[i], " Pre and Post Mindfulness Intervention", sep = "") )
ggsave(plt, filename = paste("Pre vs Post volume of ", colNames[i], ".jpg", sep=""))
print(plt)
Sys.sleep(2)
}



```

