---
title: "April10_PC_Hippo"
output: pdf_document
---

```{r}

library(readxl)
library(dplyr)
library("devtools")
library("corrplot")
library("ggplot2")
library("survival")
library("Formula")
library("lattice")
library("magrittr")
library("ggpubr")
library("plyr")
library("dplyr")
library("Matrix")
library("lme4")
library("factoextra")
library("ggfortify")
library("Hmisc")
library("tidyr")
library("lme4")
library("lmtest")
library("lmerTest")
library("emmeans")
library("car")
library("cNORM")
library("BBmisc")
library("psych")

```

```{r}
HipPC <- read_excel("~/Desktop/R/PretermControl/volumetry/Hippo_PC_Reduced.xlsx")

str(HipPC)

HipPC$Group <- as.factor(HipPC$Group)

HipPC$Gender <- as.factor(HipPC$Gender)

HipPC$Age <- as.numeric(HipPC$Age)

HipPC$Status <- as.factor(HipPC$Status)

HipPC$GA <- as.numeric(HipPC$GA)

HipPC$Pds_N <- as.numeric(HipPC$Pds_N)

str(HipPC)

#check the data for outliers
summary(HipPC)

levels(HipPC$Group)

#relevel

HipPC$Status <- relevel(HipPC$Status, ref= "Preterm")

```

```{r}

#some overall summaries

library(arsenal)

#writecsv with this table

#Again with Volumetrically Corrected Data


table_one <- tableby(Status ~ ., data= HipPC)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

tab2

write.csv(tab2, "~/Desktop/HipPCSummary.csv")



```

To Volumetrically Correct the Data

for (column.name in names(HipPC) [9:ncol(HipPC)]) {
  HipPC[column.name] = HipPC[column.name] / HipPC$ICV
}

view(HipPC)


```{r}

for (column.name in names(HipPC)[-c(1:9)]) {
  HipPC[column.name] = HipPC[column.name] / HipPC$ICV
}

head(HipPC)

```

```{r}
#testing lmer
library(lme4)

HipPC <- HipPC

head(HipPC)

```

```{r}

l1 <- lm(data= HipPC, right_Whole_hippocampus ~ Status + Age)

summary(l1)

#looping lm for entire data set

storage <- list()
for(i in names(HipPC)[-c(1:9)]){
  storage[[i]] <- lm(get(i) ~ Status, HipPC)
}


library(dplyr)
library(tidyr)
library(tidyverse)
library(devtools)


table <-  storage %>% tibble(
    dvsub = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

tab <- as.data.frame(table)

to <- subset(tab, select = -c(2))

newtable <- filter(to, term == "StatusControl")

newtable

write.csv(to, "~/Documents/HipPCpvalues.csv")

head(newtable)

pvaluec <- subset(newtable, p.value < 0.05)

pvaluec

```
Hip <-as.data.frame(HipPC[,c(9:28)])
dim(Hip)
for (i in 9:length(Hip)) { 
  variable <- Hip[,i]
  lme_cer <- lmer(variable ~ Group + ICV + (1 | Subject), data = HipPC, REML = FALSE)
print(summary(lme_cer))
}
```{r}

newtable

ordered <- newtable[order(newtable$p.value), ]

head(ordered)

write.csv(ordered, "~/Documents/HipPCorderedpvalues.csv")

pvals <- ordered$p.value

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Documents/correctionsHippoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final


write.csv(res2, "~/Documents/finalhippoPCt.csv")


```

```{r}


#effect sizes

library(effectsize)


stor <- list()
stor2 <- list()
for(i in names(HipPC)[-c(1:9)]) {
 stor[[i]] <- lm(as.formula(paste(i, "~ Status")), 
    data = HipPC)
 stor2[[i]] <- effectsize(stor[[i]])
}

stor3 <- as.data.frame(stor2)



es <- as.data.frame(t(stor3), stringsAsFactors = FALSE)



colnames(es) <- c("Intercept", "Effect_Size(Confidence_Intervals)")

head(es)

write.csv(es, "~/Desktop/PVAL/ordered/ThalPCEffectSizes.csv")


```



```{r}
#means

HipPC2 <- read_excel("~/Desktop/R/PretermControl/volumetry/Hippo_PC_Reduced.xlsx")

#means 

means <- HipPC2 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalPCmeans.csv")

filmean <- trymean[-c(1:3), ]

filmean

colnames(filmean) <- c("Mean_Preterm", "Mean_Control")

sd <- HipPC2 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/ThalPCSD.csv")

filsd <- trsd[-c(1:3), ]

colnames(filsd) <- c("SD_Preterm", "SD_Control")

filsd$SD_Post <- as.numeric(filsd$SD_Preterm)


filmean$Mean_Preterm <- paste(filmean$Mean_Preterm, filsd$SD_Preterm, sep=" ±")

filmean$Mean_Control <- paste(filmean$Mean_Control, filsd$SD_Control, sep=" ±")

filmean

colnames(filmean) <- c("Mean ± SD Preterm", "Mean ± SD Control")

filmean

write.csv(filmean, "~/Desktop/PVAL/filtered/HippoMeansSD.csv")

newtable <- cbind(filmean, newtable)

newtable

ordered2 <- newtable[order(newtable$p.value), ]

head(ordered)

pvals <- ordered$p.value

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))


finalfinal <- cbind(ordered2, FDR=round(FDR, 3))

finalfinal


write.csv(finalfinal, "~/Desktop/PVAL/final/finalfinalhippoPCt.csv")

```

iamcrying

lapply(gavtable, summary)

imcryingrn <- as.data.frame(gavtable)

imcryingrn


res.aov <- HipPC3 %>% anova_test(right_CA3_head ~ Status, covariate = ICV)
get_anova_table(res.aov)


```{r}

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)

HipPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/Hippo_PC_Reduced.xlsx")

responseList <- names(HipPC3)[-c(1:9)]

pwc1 <- list()
for (i in responseList)
  pwc1[[i]] <- HipPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Status")), covariate = "ICV",
    p.adjust.method = "fdr")


ph <-data.table::rbindlist(pwc1, fill = T)

#lets just try

ordered <-ph[order(ph$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(res2, "~/Desktop/PVAL/final/HippoPC.csv")

```


```{r}

library(emmeans)
library(rstatix)

ThalPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/Hippo_PC_Reduced.xlsx")

ThalPC3

responseList <- names(ThalPC3)[-c(1:9)]

pwc1 <- list()
for (i in responseList) 
  pwc1[[i]] <- ThalPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Status")), covariate = "ICV",
    p.adjust.method = "fdr")


ph <-data.table::rbindlist(pwc1, fill = T)

ph
means <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalPCmeans.csv")

filmean <- trymean[-c(1:3), ]

colnames(filmean) <- c("Mean_Preterm", "Mean_Control")

sd <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/HipAsymPCSD.csv")

filsd <- trsd[-c(1:3), ]

colnames(filsd) <- c("SD_Preterm", "SD_Control")

filsd$SD_Post <- as.numeric(filsd$SD_Preterm)


filmean$Mean_Preterm <- paste(filmean$Mean_Preterm, filsd$SD_Preterm, sep=" ±")

filmean$Mean_Control <- paste(filmean$Mean_Control, filsd$SD_Control, sep=" ±")

filmean

colnames(filmean) <- c("Mean ± SD Control", "Mean ± SD Preterm")

filmean

write.csv(filmean, "~/Desktop/PVAL/filtered/ThalMeansSD.csv")


#lets just try

library(effectsize)


stor <- list()
stor2 <- list()
for(i in names(ThalPC3)[-c(1:9)]) {
 stor[[i]] <- aov(as.formula(paste(i, "~ Status")), covariate = "ICV", data= ThalPC3) 
 stor2[[i]] <- effectsize(stor[[i]])
}

ees <-data.table::rbindlist(stor2, fill = T)

ees

phh <- cbind(filmean, ph, ees)

phh

##


ordered <-phh[order(phh$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/hippoASymFINAL.csv")

```



storage <- list()
iamcrying <- list()
for(i in names(HipPC3)[-c(1:9)]) {
  storage[[i]] <- HipPC3 %>% anova_test(as.formula(paste(i, "~ ICV + Status")))
  iamcrying[[i]] <- get_anova_table(storage[[i]])
}

```{r}

("~/Desktop/R/PretermControl/volumetry/Hippo_PC_Reduced.xlsx")

responseList <- names(HipPC3)[-c(1:9)]
for(n in responseList) {
  anova2 <- aov(get(n) ~ ICV + Status, data = HipPC3)
  summary(anova2)
  wt_emm2 <- emmeans(anova2, "ICV")
  output[[n]] <- pairs(wt_emm2)
}

output
  

library(tidyverse)
  library(emmeans)
  
vector(mode = "list", length = N)

pwc <- vector(mode ="list")
output <-list()
for (i in names(HipPC3)[-c(1:9)]) { 
  pwc[[i]] <- HipPC3 %>% emmeans_test(as.formula(paste(i, "~ Status")), covariate = ICV,
    p.adjust.method = "fdr") 
  output[[n]] <- pairs(pwc)}

responseList <- names(HipPC3)[-c(1:9)]


modelList  <- lapply(responseList, function(resp) {
  mF <- formula(paste(resp, " ~ ICV + Status"))
  aov(mF, data = HipPC3)
})

modelList

summary(modelList)
modelList  <- lapply(responseList, function(aov) {
  mF <- formula(paste(aov, " ~ ICV + Status"))
  av <- aov(mF, data = HipPC3)
  attr(av, 'call')$formula <- mF
  av
})

modelList

modelList2 <- lapply(modelList, function(x) pairs(emmeans(x, "ICV")))

modelList2

pwc

pls <- lapply(pwc, summary)

pls

pwdata <- as.data.frame(pwc)

trydf <- as.data.frame(pwc1, stringsAsFactors = FALSE)

trydf

pwdata <-as.data.frame(t(pwc1), stringsAsFactors = FALSE)

pwdata


pwc %>% separate()

t <- summary(pwc)

View(t)

library(tidyverse)

aov.models = HipPC3[ , -grep("cyl", names(mtcars))] %>%
  map(~ aov(mtcars$cyl ~ .x))


aov.models = df[ , -grep("PGY_16", names(df))] %>%
  map(~ aov(df$PGY_16 ~ .x))


HipPC3$Group <- as.factor(HipPC$Group)

HipPC3$Gender <- as.factor(HipPC$Gender)

HipPC3$Age <- as.numeric(HipPC$Age)

HipPC3$Status <- as.factor(HipPC$Status)

HipPC3$GA <- as.numeric(HipPC$GA)

HipPC3$Pds_N <- as.numeric(HipPC$Pds_N)

sapply(HipPC3,class)

HipPC3$Subject <- unlist(HipPC3$Subject)

HipPC3$Exp <- unlist(HipPC3$Exp)

for(i in responseList)
  {
column <- responseList
avz <- broom::tidy(aov(as.formula(paste(i, "~ Status", data = HipPC3))))
}

rlang::last_error()

pwdata

pwc <- list()
for (i in names(HipPC3)[-c(1:9)]) { 
  pwc[[i]] <- HipPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Status")), covariate = ICV,
    p.adjust.method = "fdr") }

pwc

print(pwc)

write.csv(pwc, "~/Desktop/PVAL/final/cryingt.csv")

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)



avz <- broom::tidy(aov(df[,i] ~ group, data = df))



pwc

trydf

lapply(split(trydf, by="term", keep.by=FALSE), unlist, use.names=FALSE)

gavtable

View(gavtable)

```