---
title: "nepsy-nepsyeic"
output: pdf_document
---

PREPOST VOLUMETRY CODE 


```{r}

library(readxl)
library(dplyr)
library("devtools")
library("corrplot")
library("ggplot2")
library("survival")
library("Formula")
library("lattice")
library("magrittr")
library("ggpubr")
library("plyr")
library("dplyr")
library("Matrix")
library("lme4")
library("factoextra")
library("ggfortify")
library("Hmisc")
library("tidyr")
library("lme4")
library("lmtest")
library("lmerTest")
library("emmeans")
library("car")
library("cNORM")
library("BBmisc")
library("psych")

```

```{r}
nepsyeicPrePost <- read_excel("~/Desktop/R/PrePost/Neuropsych/NEPSY-EIC.xlsx")
   

str(nepsyeicPrePost)

nepsyeicPrePost$Group <- as.factor(nepsyeicPrePost$Group)

nepsyeicPrePost$Gender <- as.factor(nepsyeicPrePost$Gender)

nepsyeicPrePost$Age <- as.numeric(nepsyeicPrePost$Age)

str(nepsyeicPrePost)

#check the data for outliers
summary(nepsyeicPrePost)

levels(nepsyeicPrePost$Group)

#relevel

nepsyeicPrePost$Group <- relevel(nepsyeicPrePost$Group, ref= "Pre")

```

```{r}

#some overall summaries

library(arsenal)

#writecsv with this table

#Again with Volumetrically Corrected Data


table_one <- tableby(Group ~ ., data= nepsyeicPrePost)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

tab2

write.csv(tab2, "~/Desktop/nepsyeicPrePostSummary.csv")

nepsyeicPrePost


```

To Volumetrically Correct the Data

for (column.name in names(nepsyeicPrePost) [9:ncol(nepsyeicPrePost)]) {
  nepsyeicPrePost[column.name] = nepsyeicPrePost[column.name] / nepsyeicPrePost$ICV
}

view(nepsyeicPrePost)


```{r}

#testing lmer
library(lme4)

model <- lmer(TN ~ Group + (1 | ID), data = nepsyeicPrePost, REML = FALSE)

##tring to do a paired sample t.test


library(dplyr)


#visualize data using boxplots

library("PairedData")

# Subset vol data before treatment
before <- subset(nepsyeicPrePost,  Group == "Pre", TN,
                 drop = TRUE)
# subset weight data after treatment
after <- subset(nepsyeicPrePost,  Group == "Post", TN,
                 drop = TRUE)

# Plot paired data
library(PairedData)
pd <- paired(before, after)
plot(pd, type = "profile") + theme_bw()

ggplot(data=nepsyeicPrePost) + aes(x= Group, y= TN, colour= Group) + geom_boxplot()


##checking normality 

# compute the difference
d <- with(nepsyeicPrePost, 
        TN[Group == "Pre"] - TN[Group == "Post"])
d

# Shapiro-Wilk normality test for the differences
shapiro.test(d) # => p-value = 0.4

#pvalue above 0.05 means that we can assume normality

qqplot <- qqnorm(nepsyeicPrePost$TN, pch = 1, frame = FALSE)

histogram(nepsyeicPrePost$TN)

#nowt.test (if we were to assume normality) #cant use here since we havent volumetrically corrected the data and need to add it as covariate

res <- t.test(TN ~ Group, nepsyeicPrePost, paired = TRUE)
res

#lmer results

summary(model)

##plot the data

ggplot(nepsyeicPrePost) + aes(x= Group, y = TN, color= Group) + geom_boxplot() + labs(title= "Volume of Left Lateral Nucleus Pre and Post Mindfulness Intervention", x= "Intervention Group", y= "Volume") 


##Now we use the final lmer formula

fit.compact = lmer(formula = TN ~ Group + Age + Gender + (1 | ID),
                   data = nepsyeicPrePost)
fit.augmented = lmer(formula = TN ~ Group +  (1 | ID),
                     data = nepsyeicPrePost)

# compare via Chisq-test
anova(fit.compact, fit.augmented)
```
nepsyeic <-as.data.frame(nepsyeicPrePost[,c(9:28)])
dim(nepsyeic)
for (i in 9:length(nepsyeic)) { 
  variable <- nepsyeic[,i]
  lme_cer <- lmer(variable ~ Group + ICV + (1 | Subject), data = nepsyeicPrePost, REML = FALSE)
print(summary(lme_cer))
}
```{r}

library(dplyr)
library(tidyr)
library(tidyverse)
library(devtools)
library(broom.mixed)
library(lmerTest)

storage <- list()
for(i in names(nepsyeicPrePost)[-c(1:7)]){
  storage[[i]] <- lmer(get(i) ~ Group + NB_SDQ_HA + (1 | ID), data= nepsyeicPrePost, REML = FALSE)
}

library(lme4)
library(broom)
library(broomExtra)

table <-  storage %>% tibble(
    dvsub = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

tab <- as.data.frame(table)

to <- subset(tab, select = -c(2))

to

newtable <- filter(to, term == "GroupPost")

write.csv(to, "~/Documents/nepsyeicasymmetrypvalues.csv")

head(newtable)

View(pvaluecheck)

pvaluec <- subset(newtable, p.value < 0.1)

pvaluec

#rightBasalnucleus

a <- lmer(NB_SDQ_HA ~ Group +  (1 | ID), data= nepsyeicPrePost)

summary(a)

```


```{r}

#means 

means <- nepsyeicPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/nepsyeicmeans.csv")

filmean <- trymean[-c(1:4), ]

filmean

colnames(filmean) <- c("Mean_Preterm", "Mean_Control")

sd <- nepsyeicPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/nepsyeicSD.csv")

filsd <- trsd[-c(1:4), ]

colnames(filsd) <- c("SD_Preterm", "SD_Control")

filsd$SD_Post <- as.numeric(filsd$SD_Preterm)


filmean$Mean_Preterm <- paste(filmean$Mean_Preterm, filsd$SD_Preterm, sep=" ±")

filmean$Mean_Control <- paste(filmean$Mean_Control, filsd$SD_Control, sep=" ±")

filmean

colnames(filmean) <- c("Mean ± SD Pre", "Mean ± SD Post")

filmean

write.csv(filmean, "~/Desktop/PVAL/filtered/ThalMeansSD.csv")

newtable <- cbind(filmean, newtable)

newtable

```


```{r}


ordered <- newtable[order(newtable$p.value), ]

write.csv(ordered, "~/Documents/nepsyeicyorderedpvalues.csv")

pvals <- ordered$p.value

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Documents/correctionsei.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/finalnepsyeic.csv")


```
