---
title: "Thalamus_PrePost_April7"
output: pdf_document
---



```{r}

library(readxl)
library(dplyr)
library("devtools")
library("corrplot")
library("ggplot2")
library("survival")
library("Formula")
library("lattice")
library("magrittr")
library("ggpubr")
library("plyr")
library("dplyr")
library("Matrix")
library("lme4")
library("factoextra")
library("ggfortify")
library("Hmisc")
library("tidyr")
library("lme4")
library("lmtest")
library("lmerTest")
library("emmeans")
library("car")
library("cNORM")
library("BBmisc")
library("psych")

```

```{r}
ThalmPrePost <- read_excel("~/Desktop/R/PrePost/Regular/ThalamusPrePost.xlsx")

str(ThalmPrePost)

ThalmPrePost$Group <- as.factor(ThalmPrePost$Group)

ThalmPrePost$Gender <- as.factor(ThalmPrePost$Gender)

ThalmPrePost$Age <- as.numeric(ThalmPrePost$Age)

str(ThalmPrePost)

#check the data for outliers
summary(ThalmPrePost)

levels(ThalmPrePost$Group)

#relevel

ThalmPrePost$Group <- relevel(ThalmPrePost$Group, ref= "Pre")

```

```{r}

#some overall summaries

library(arsenal)

#writecsv with this table

#Again with Volumetrically Corrected Data


table_one <- tableby(Group ~ ., data= ThalmPrePost)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

tab2

write.csv(tab2, "~/Desktop/TableOne/ThalmPrePostSummary.csv")



```

To Volumetrically Correct the Data

for (column.name in names(ThalmPrePost) [9:ncol(ThalmPrePost)]) {
  ThalmPrePost[column.name] = ThalmPrePost[column.name] / ThalmPrePost$ICV
}

view(ThalmPrePost)

```{r}

#means

means <- ThalmPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalPrePostmeans.csv")

filmean <- trymean[-c(1:5), ]

filmean

colnames(filmean) <- c("Mean_Pre", "Mean_Post")

sd <- ThalmPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/ThalPrePostSD.csv")

filsd <- trsd[-c(1:5), ]

colnames(filsd) <- c("SD_Pre", "SD_Post")

filsd$SD_Post <- as.numeric(filsd$SD_Post)

filmean$SD_Post <- filsd$SD_Post

filmean$SD_Pre <- filsd$SD_Pre

filmean




```


```{r}

for (column.name in names(ThalmPrePost) [9:ncol(ThalmPrePost)]) {
  ThalmPrePost[column.name] = ThalmPrePost[column.name] / ThalmPrePost$ICV
}

ThalmPrePost

```

```{r}
#testing lmer
library(lme4)

model <- lmer(Left_LGN ~ Group + (1 | Subject), data = ThalmPrePost, REML = FALSE)



##tring to do a paired sample t.test


library(dplyr)


#visualize data using boxplots

library("PairedData")

# Subset vol data before treatment
before <- subset(ThalmPrePost,  Group == "Pre", Left_LGN,
                 drop = TRUE)
# subset weight data after treatment
after <- subset(ThalmPrePost,  Group == "Post", Left_LGN,
                 drop = TRUE)

# Plot paired data
library(PairedData)
pd <- paired(before, after)
plot(pd, type = "profile") + theme_bw()

ggplot(data=ThalmPrePost) + aes(x= Group, y= Left_LGN, colour= Group) + geom_boxplot()


##checking normality 

# compute the difference
d <- with(ThalmPrePost, 
        Left_LGN[Group == "Pre"] - Left_LGN[Group == "Post"])
d

# Shapiro-Wilk normality test for the differences
shapiro.test(d) # => p-value = 0.4

#pvalue above 0.05 means that we can assume normality

qqplot <- qqnorm(ThalmPrePost$Left_LGN, pch = 1, frame = FALSE)

histogram(ThalmPrePost$Left_LGN)

#nowt.test (if we were to assume normality) #cant use here since we havent volumetrically corrected the data and need to add it as covariate

res <- t.test(Left_LGN ~ Group, ThalmPrePost, paired = TRUE)
res

#lmer results

summary(model)

##plot the data

ggplot(ThalmPrePost) + aes(x= Group, y = Left_LGN, color= Group) + geom_boxplot() + labs(title= "Volume of Left Lateral Nucleus Pre and Post Mindfulness Intervention", x= "Intervention Group", y= "Volume") 


##Now we use the final lmer formula

fit.compact = lmer(formula = Left_LGN ~ Group + ICV + Age + Gender + (1 | Subject),
                   data = ThalmPrePost)
fit.augmented = lmer(formula = Left_LGN ~ Group + ICV + (1 | Subject),
                     data = ThalmPrePost)

# compare via Chisq-test
anova(fit.compact, fit.augmented)
```
Thalm <-as.data.frame(ThalmPrePost[,c(9:28)])
dim(Thalm)
for (i in 9:length(Thalm)) { 
  variable <- Thalm[,i]
  lme_cer <- lmer(variable ~ Group + ICV + (1 | Subject), data = ThalmPrePost, REML = FALSE)
print(summary(lme_cer))
}
```{r}

library(dplyr)
library(tidyr)
library(tidyverse)
library(devtools)
library(broom.mixed)
library(lmerTest)

storage <- list()
for(i in names(ThalmPrePost)[-c(1:8)]){
  storage[[i]] <- lmer(get(i) ~ Group + (1 | Subject), data= ThalmPrePost, REML = FALSE)
}

library(lme4)
library(broom)
library(broomExtra)

table <-  storage %>% tibble(
    dvsub = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

tab <- as.data.frame(table)

to <- subset(tab, select = -c(2))

newtable <- filter(to, term == "GroupPost")

newtable

newtable2 <- cbind(filmean, newtable)

newtable2

write.csv(to, "~/Desktop/PVAL/ALL/ThalmPrePostvalues.csv")
write.csv(newtable, "~/Desktop/PVAL/filtered/ThalmPostpvalues.csv")

head(newtable2)


pvaluec <- subset(newtable2, p.value < 0.05)

pvaluec

pvals <- newtable2$p.value



```

```{r}


#bonferroni corrections

ordered <- newtable2[order(newtable$p.value), ]

ordered

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalmPrePostorderedpvalues.csv")

pvals <- ordered$p.value

pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalPrePostsymmetry.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/finalthalprepost.csv")



```