---
title: "Thalamus_Aymmetry_PrePost"
output: pdf_document
---

```{r}

library(readxl)
library(dplyr)
library("devtools")
library("corrplot")
library("ggplot2")
library("survival")
library("Formula")
library("lattice")
library("magrittr")
library("ggpubr")
library("plyr")
library("dplyr")
library("Matrix")
library("lme4")
library("factoextra")
library("ggfortify")
library("Hmisc")
library("tidyr")
library("lme4")
library("lmtest")
library("lmerTest")
library("emmeans")
library("car")
library("cNORM")
library("BBmisc")
library("psych")

```

```{r}
ThalAsymPrePost <- read_excel("~/Desktop/R/PrePost/Asymmetry/Final_Thalamus_PrePost_Asymm.xlsx")
str(ThalAsymPrePost)

ThalAsymPrePost$Group <- as.factor(ThalAsymPrePost$Group)

ThalAsymPrePost$Gender <- as.factor(ThalAsymPrePost$Gender)

ThalAsymPrePost$Age <- as.numeric(ThalAsymPrePost$Age)

str(ThalAsymPrePost)

#check the data for outliers
summary(ThalAsymPrePost)

levels(ThalAsymPrePost$Group)

#relevel

ThalAsymPrePost$Group <- relevel(ThalAsymPrePost$Group, ref= "Pre")

```

```{r}

#some overall summaries

library(arsenal)

#writecsv with this table

#Again with Volumetrically Corrected Data


table_one <- tableby(Group ~ ., data= ThalAsymPrePost)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

tab2

write.csv(tab2, "~/Desktop/TableOne/ThalAsymPrePostSummary.csv")



```

To Volumetrically Correct the Data

for (column.name in names(ThalAsymPrePost) [9:ncol(ThalAsymPrePost)]) {
  ThalAsymPrePost[column.name] = ThalAsymPrePost[column.name] / ThalAsymPrePost$ICV
}

view(ThalAsymPrePost)


```{r}


#means

means <- ThalAsymPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalAsymPrePostmeans.csv")

filmean <- trymean[-c(1:5), ]

filmean

colnames(filmean) <- c("Mean_Pre", "Mean_Post")

sd <- ThalAsymPrePost %>%
  group_by(Group) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/ThalAsymPrePostSD.csv")

filsd <- trsd[-c(1:5), ]

colnames(filsd) <- c("SD_Pre", "SD_Post")

filsd$SD_Post <- as.numeric(filsd$SD_Post)

filmean$SD_Post <- filsd$SD_Post

filmean$SD_Pre <- filsd$SD_Pre

filmean


```


```{r}

#testing lmer
library(lme4)

model <- lmer(LGN ~ Group + Age + (1 | Subject), data = ThalAsymPrePost, REML = FALSE)

##tring to do a paired sample t.test


library(dplyr)


#visualize data using boxplots

library("PairedData")

# Subset vol data before treatment
before <- subset(ThalAsymPrePost,  Group == "Pre", Lateralnucleus,
                 drop = TRUE)
# subset weight data after treatment
after <- subset(ThalAsymPrePost,  Group == "Post", Lateralnucleus,
                 drop = TRUE)

# Plot paired data
library(PairedData)

ggplot(data=ThalAsymPrePost) + aes(x= Group, y= Lateralnucleus, colour= Group) + geom_boxplot()


##checking normality 

# compute the difference
d <- with(ThalAsymPrePost, 
        Lateralnucleus[Group == "Pre"] - Lateralnucleus[Group == "Post"])
d

# Shapiro-Wilk normality test for the differences
shapiro.test(d) # => p-value = 0.4

#pvalue above 0.05 means that we can assume normality

qqplot <- qqnorm(ThalAsymPrePost$Lateralnucleus, pch = 1, frame = FALSE)

histogram(ThalAsymPrePost$Lateralnucleus)

#nowt.test (if we were to assume normality) #cant use here since we havent volumetrically corrected the data and need to add it as covariate

res <- t.test(Lateralnucleus ~ Group, ThalAsymPrePost, paired = TRUE)
res

#lmer results

summary(model)

##plot the data

ggplot(ThalAsymPrePost) + aes(x= Group, y = Lateralnucleus, color= Group) + geom_boxplot() + labs(title= "Volume of Left Lateral Nucleus Pre and Post Mindfulness Intervention", x= "Intervention Group", y= "Volume") 


##Now we use the final lmer formula

fit.compact = lmer(formula = Lateralnucleus ~ Group + Age + Gender + (1 | Subject),
                   data = ThalAsymPrePost)
fit.augmented = lmer(formula = Lateralnucleus ~ Group + (1 | Subject),
                     data = ThalAsymPrePost)

# compare via Chisq-test
anova(fit.compact, fit.augmented)
```
Thal <-as.data.frame(ThalAsymPrePost[,c(9:28)])
dim(Thal)
for (i in 9:length(Thal)) { 
  variable <- Thal[,i]
  lme_cer <- lmer(variable ~ Group + ICV + (1 | Subject), data = ThalAsymPrePost, REML = FALSE)
print(summary(lme_cer))
}
```{r}

library(dplyr)
library(tidyr)
library(tidyverse)
library(devtools)
library(broom.mixed)
library(lmerTest)

storage <- list()
for(i in names(ThalAsymPrePost)[-c(1:8)]){
  storage[[i]] <- lmer(get(i) ~ Group + (1 | Subject), data= ThalAsymPrePost, REML = FALSE)
}

library(lme4)
library(broom)
library(broomExtra)

table <-  storage %>% tibble(
    dvsub = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

tab <- as.data.frame(table)

to <- subset(tab, select = -c(2))

newtable <- filter(to, term == "GroupPost")

newtable

write.csv(to, "~/Desktop/PVAL/filtered/Thalasymmetrypvalues.csv")

head(newtable)

pvaluec <- subset(newtable, p.value < 0.05)

pvaluec

#no significant 
```
```{r}

library(effectsize)

stor <- list()
stor2 <- list()
for(i in names(ThalAsymPrePost)[-c(1:9)]) {
 stor[[i]] <- lmer(as.formula(paste(i, "~ Group + (1|Subject)")), 
    data = ThalAsymPrePost)
 stor2[[i]] <- effectsize(stor[[i]]) }

ees <-data.table::rbindlist(stor2, fill = T)

ees

phh <- cbind(filmean, ph, ees)

phh

##


```

```{r}

#testing the normality of the residuals pt 2?

#bonferroni corrections

newtable2 <- cbind(filmean, newtable)

newtable2

ordered <- newtable2[order(newtable2$p.value), ]
ordered

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPrePostasymmetryorderedpvalues.csv")

pvals <- ordered$p.value

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalPrePostaasymmetry.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/finalThalPrePostasymmprepost.csv")

```


```{r}

library(emmeans)
library(rstatix)

ThalPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/Thalamus_PC_Reduced.xlsx")

ThalPC3

responseList <- names(ThalPC3)[-c(1:8)]

pwc1 <- list()
for (i in responseList) {
  pwc1[[i]] <- ThalPC3 %>% 
  lmer(as.formula(paste(i, "~ Group + (1 | Subject)"), data= ThalAsymPrePost, REML = FALSE)}
                  


ph <-data.table::rbindlist(pwc1, fill = T)

ph
means <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalPCmeans.csv")

filmean <- trymean[-c(1:2), ]

colnames(filmean) <- c("Mean_Preterm", "Mean_Control")

sd <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/HipAsymPCSD.csv")

filsd <- trsd[-c(1:2), ]

colnames(filsd) <- c("SD_Preterm", "SD_Control")

filsd$SD_Post <- as.numeric(filsd$SD_Preterm)


filmean$Mean_Preterm <- paste(filmean$Mean_Preterm, filsd$SD_Preterm, sep=" ±")

filmean$Mean_Control <- paste(filmean$Mean_Control, filsd$SD_Control, sep=" ±")

filmean

colnames(filmean) <- c("Mean ± SD Control", "Mean ± SD Preterm")

filmean

write.csv(filmean, "~/Desktop/PVAL/filtered/ThalMeansSD.csv")


#lets just try

library(effectsize)


stor <- list()
stor2 <- list()
for(i in names(ThalPC3)[-c(1:8)]) {
 stor[[i]] <- aov(as.formula(paste(i, "~ Status")), covariate = "ICV", data= ThalPC3) 
 stor2[[i]] <- effectsize(stor[[i]])
}

ees <-data.table::rbindlist(stor2, fill = T)

ees

phh <- cbind(filmean, ph, ees)

phh

##


ordered <-phh[order(phh$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/hippoASymFINAL.csv")

```