---
title: "Thalm_PC_VC"
output: pdf_document
---
```{r}

library(readxl)
library(dplyr)
library("devtools")
library("corrplot")
library("ggplot2")
library("survival")
library("Formula")
library("lattice")
library("magrittr")
library("ggpubr")
library("plyr")
library("dplyr")
library("Matrix")
library("lme4")
library("factoextra")
library("ggfortify")
library("Hmisc")
library("tidyr")
library("lme4")
library("lmtest")
library("lmerTest")
library("emmeans")
library("car")
library("cNORM")
library("BBmisc")
library("psych")

```

```{r}
ThalPC <- read_excel("~/Desktop/R/PretermControl/volumetry/Thalamus_PC_Reduced.xlsx")

str(ThalPC)

ThalPC$Group <- as.factor(ThalPC$Group)

ThalPC$Gender <- as.factor(ThalPC$Gender)

ThalPC$Age <- as.numeric(ThalPC$Age)

ThalPC$Status <- as.factor(ThalPC$Status)

ThalPC$GA <- as.numeric(ThalPC$GA)

ThalPC$Pds_N <- as.numeric(ThalPC$Pds_N)

str(ThalPC)

#check the data for outliers
summary(ThalPC)

levels(ThalPC$Group)

#relevel

ThalPC$Status <- relevel(ThalPC$Status, ref= "Preterm")

```

```{r}

#some overall summaries

library(arsenal)



table_one <- tableby(Status ~ ., data= ThalPC)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

tab2

write.csv(tab2, "~/Desktop/TableOne/ThalPCSummary.csv")



```

for (column.name in names(ThalPC) [9:ncol(ThalPC)]) {
  ThalPC[column.name] = ThalPC[column.name] / ThalPC$ICV
}



```{r}

#means 

means <- ThalPC %>%
  group_by(Status) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalPCmeans.csv")

filmean <- trymean[-c(1:5), ]

filmean

colnames(filmean) <- c("Mean_Preterm", "Mean_Control")

sd <- ThalPC %>%
  group_by(Status) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/ThalPCSD.csv")

filsd <- trsd[-c(1:5), ]

colnames(filsd) <- c("SD_Preterm", "SD_Control")

filsd$SD_Post <- as.numeric(filsd$SD_Preterm)


filmean$Mean_Preterm <- paste(filmean$Mean_Preterm, filsd$SD_Preterm, sep=" ±")

filmean$Mean_Control <- paste(filmean$Mean_Control, filsd$SD_Control, sep=" ±")

filmean

colnames(filmean) <- c("Mean ± SD Preterm", "Mean ± SD Control")

filmean

write.csv(filmean, "~/Desktop/PVAL/filtered/ThalMeansSD.csv")

```

```{r}

#volumetric corrections

for (column.name in names(ThalPC)[10:ncol(ThalPC)]) {
  ThalPC[column.name] = ThalPC[column.name] / ThalPC$ICV
}

head(ThalPC)


```


```{r}
#testing lmer
library(lme4)
library(dplyr)
library(tibble)

l1 <- lm(data= ThalPC, Left_LGN ~ Status*ICV)

summary(l1)

#looping lm for entire data set

storage <- list()
for(i in names(ThalPC)[-c(1:9)]){
  storage[[i]] <- lm(get(i) ~ Status, ThalPC)
}

library(dplyr)
library(tidyr)
library(tidyverse)
library(devtools)


table <-  storage %>% tibble(
    dvsub = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

tab <- as.data.frame(table)

to <- subset(tab, select = -c(2))


newtable <- filter(to, term == "StatusControl")

newtable

write.csv(to, "~/Desktop/PVAL/filtered/ThalPCpvalues.csv")


```


storage2 <- list()
for(i in seq_along(tl)) {
  tl[i] <- lm(data= ThalPC, tl[i] ~ Status)
  storage[[i]] <- lm(get(i) ~ Status, ThalPC)
pls <- effectsize(tl[i])}

tl <- names(ThalPC)[-c(1:9)]

stor3 <- list()
for(i in names(ThalPC)[-c(1:9)]) {
 stor3[[i]] <- effectsize(lm(as.formula(paste(i, "~ Status"))), 
    data = ThalPC)}

```{r}

#effect sizes

library(effectsize)

head(ThalPC)

stor <- list()
stor2 <- list()
for(i in names(ThalPC)[-c(1:9)]) {
 stor[[i]] <- aov(as.formula(paste(i, "~ Status")), data=ThalPC) 
 stor2[[i]] <- effectsize(stor[[i]])
}

ees <-data.table::rbindlist(stor2, fill = T)


write.csv(es, "~/Desktop/PVAL/ordered/ThalPCEffectSizes.csv")


ees


```


```{r}
newtable

pvaluec <- subset(newtable, p.value < 0.05)

pvaluec

newtable2 <- cbind(filmean, newtable)

newtable2


```
Thal <-as.data.frame(ThalPC[,c(9:28)])
dim(Thal)
for (i in 9:length(Thal)) { 
  variable <- Thal[,i]
  lme_cer <- lmer(variable ~ Group + ICV + (1 | Subject), data = ThalPC, REML = FALSE)
print(summary(lme_cer))
}
```{r}


ordered <- newtable2[order(newtable2$p.value), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPCorderedpvalues.csv")

pvals <- ordered$p.value
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final


```

```{r}

write.csv(final, "~/Desktop/PVAL/final/finalThalpoPCt.csv")


colNames <- names(ThalPC)[-c(1:8)]

ggplot(ThalPC, aes(x= Status, y = ICV, color= Status)) + geom_boxplot() + theme_classic() + labs(title= "Volume of Left_LGN In VPT Children vs Controls", x= "Group", y= "Volume")

#all graphs

seq_along(colNames)

for(i in seq_along(colNames)) {
plt<- ggplot(ThalPC, aes_string(x= "Status", y = colNames[i], color= "Status")) + geom_boxplot() + theme_classic() + labs(x= "Group", y= "Volume", title= paste("Volume of ", colNames[i], " in VPT Children vs Controls", sep = "") )
print(plt)
ggsave(plt, filename = paste("VPT vs CT volume of ", colNames[i], ".jpg", sep=""))
Sys.sleep(2)
}


library(rlang)
library(tidyverse)

```


```{r}

#trying to extract only significant graphs 

fdrsig <- subset(ordered, FDR < 0.1)

fdrsig

nm <- fdrsig$dvsub

nm


for(i in seq_along(nm)) {
plt<- ggplot(ThalPC, aes_string(x= "Status", y = nm[i], color= "Status")) + geom_boxplot() + theme_classic() + labs(x= "Group", y= "Volume", title= paste("Volume of ", nm[i], " in VPT Children vs Controls", sep = "") )
print(plt)
ggsave(plt, filename = paste("Sig VPT vs CT volume of ", nm[i], ".jpg", sep=""))
Sys.sleep(2)
}


for(i in seq_along(nm)) {
plt<- ggplot(ThalPC, aes_string(x= "Pds_N", y = nm[i])) + geom_point() + geom_smooth(method="glm") + geom_jitter() + theme_classic() + labs(x= "Group", y= "Volume", title= paste("Volume of ", nm[i], " by birthweight in VPT Children vs Controls", sep = "") )
print(plt)
Sys.sleep(2)
}


```


```{r}
library(anova)


storage <- list()
gavtable <- list()
for(i in names(ThalPC)[-c(1:9)]) {
  storage[[i]] <- ThalPC %>% anova_test(as.formula(paste(i, "~ ICV + Status")))
  gavtable[[i]] <- get_anova_table(storage[[i]])
}

gavtable

View(gavtable)



```


```{r}

library("afex")     # needed for ANOVA functions.
library("emmeans")  # emmeans must now be loaded explicitly for follow-up tests.
library("multcomp") # for advanced control for multiple testing/Type 1 errors.
library("ggplot2")

ThalPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/Thalamus_PC_Reduced.xlsx")
responseList <- names(ThalPC3)[-c(1:9)]

av <- list()
for (i in responseList)
av[[i]] <- ThalPC3 %>% anova_test(as.formula(paste(i, "~ ICV + Status")))


ah <-data.table::rbindlist(av, fill = T)

ah

ah2 <- filter(ah, Effect == "Status")

ah <- ah2

ah

ordered2 <-ah[order(ah$p), ]

head(ordered2)

write.csv(ordered2, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals2 <- ordered2$p
pvals2

FDR = p.adjust(pvals2, "fdr")
res = cbind(pvals2, FDR=round(FDR, 3))

res

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final2 <- cbind(ordered2, FDR=round(FDR, 3))

final2



```
  read.csv("~/Desktop/R/PretermControl/volumetry/Thalamus_PC_Reduced.xlsx", sep= ",")
```{r}
library(emmeans)
library(rstatix)

ThalPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/Thalamus_PC_Reduced.xlsx")

ThalPC3

responseList <- names(ThalPC3)[-c(1:9)]

pwc1 <- list()
for (i in responseList) 
  pwc1[[i]] <- ThalPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Status")), covariate= "ICV",
    p.adjust.method = "fdr")


ph <-data.table::rbindlist(pwc1, fill = T)

ph

#lets just try

library(effectsize)


stor <- list()
stor2 <- list()
for(i in names(ThalPC3)[-c(1:8)]) {
 stor[[i]] <- aov(as.formula(paste(i, "~ Status")), covariate= "ICV", data= ThalPC3) 
 stor2[[i]] <- effectsize(stor[[i]])
}

ees <-data.table::rbindlist(stor2, fill = T)

ees

phh <- cbind(ph, ees)

phh

##


ordered <-ph[order(ph$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/fdr/THALPCFINAL.csv")


```

```{r}

ThalPC <- read_excel("~/Desktop/R/PretermControl/volumetry/Thalamus_PC_Reduced.xlsx")

responseList <- names(ThalPC)[-c(1:)]

res.aov <- ThalPC %>% 
  anova_test(Left_CeM ~ ICV + Status*Pds_N)


test <- ThalPC %>% 
  group_by(Pds_N) %>%
  emmeans_test(Left_CeM ~ Status, p.adjust.method = "fdr")

test

pwc1 <- list()
for (i in responseList) 
  pwc1[[i]] <- ThalPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Pds_N")), covariate = "ICV",
    p.adjust.method = "fdr")


ph <-data.table::rbindlist(pwc1, fill = T)

ph

#lets just try

ordered <-ph[order(ph$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final



```

```{r}
library(emmeans)
library(rstatix)

ThalPC3 <- read_excel("~/Desktop/R/PretermControl/volumetry/Thalamus_PC_Reduced.xlsx")

ThalPC3
str(ThalPC3)

lm1 <- lm(data=ThalPC3, ICV ~ Status)

summary(lm1)

responseList <- names(ThalPC3)[-c(1:9)]

pwc1 <- list()
for (i in responseList) 
  pwc1[[i]] <- ThalPC3 %>% 
  emmeans_test(as.formula(paste(i, "~ Status")), covariate = "ICV",
    p.adjust.method = "fdr")


ph <-data.table::rbindlist(pwc1, fill = T)

ph
means <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, mean)

trymean <- as.data.frame(t(means), stringsAsFactors = FALSE)
trymean

write.csv(trymean, "~/Desktop/PVAL/filtered/ThalPCmeans.csv")

filmean <- trymean[-c(1:3), ]

colnames(filmean) <- c("Mean_Preterm", "Mean_Control")

sd <- ThalPC3 %>%
  group_by(Status) %>%
  summarise_if(is.numeric, SD)

sd
trsd <- as.data.frame(t(sd), stringsAsFactors = FALSE)
trsd

write.csv(trsd, "~/Desktop/PVAL/filtered/HipAsymPCSD.csv")

filsd <- trsd[-c(1:3), ]

colnames(filsd) <- c("SD_Preterm", "SD_Control")

filsd$SD_Post <- as.numeric(filsd$SD_Preterm)


filmean$Mean_Preterm <- paste(filmean$Mean_Preterm, filsd$SD_Preterm, sep=" ±")

filmean$Mean_Control <- paste(filmean$Mean_Control, filsd$SD_Control, sep=" ±")

filmean

colnames(filmean) <- c("Mean ± SD Control", "Mean ± SD Preterm")

filmean

write.csv(filmean, "~/Desktop/PVAL/filtered/ThalMeansSD.csv")


#lets just try

library(effectsize)


stor <- list()
stor2 <- list()
for(i in names(ThalPC3)[-c(1:9)]) {
 stor[[i]] <- aov(as.formula(paste(i, "~ Status")), covariate = "ICV", data= ThalPC3) 
 stor2[[i]] <- effectsize(stor[[i]])
}

ees <-data.table::rbindlist(stor2, fill = T)

ees

phh <- cbind(filmean, ph, ees)

phh

##


ordered <-phh[order(phh$p), ]

head(ordered)

write.csv(ordered, "~/Desktop/PVAL/ordered/ThalPC3orderedpvalues.csv")

pvals <- ordered$p
pvals

FDR = p.adjust(pvals, "fdr")
res2 = cbind(pvals, FDR=round(FDR, 3))

res2

write.csv(res2, "~/Desktop/PVAL/fdr/correctionsThalpoPC.csv")

final <- cbind(ordered, FDR=round(FDR, 3))

final

write.csv(final, "~/Desktop/PVAL/final/ThalAsymFINAL.csv")

```




```{r}
head(ThalPC)





lm

storage <- list()
gorage <- list()
for(i in names(ThalPC3)[-c(1:9)]) {
  storage[[i]] <- lm(get(i) ~ Status, ThalPC)
  gorage[[i]] <- effectsize((storage[[i]]))
}

effectsize(lm2)

stor[[i]]

for (i in names (ThalPC)[-c(1:9)]) {
  storage[[i]] <- lm(get(i) ~ Status, ThalPC)
  print(storage[[i]])}

n <- names(ThalPC)[-c(1:9)]

for (i in seq_along(n)) {
  effectsize(lm(i ~ Status, ThalPC)) }


View(ThalPC)

lm2 <- lm(Right_Pf ~ Status, ThalPC)

lm2

effectsize(lm(Right_Pf~ Status, ThalPC))


summary(lm1)

effectsize(lm1)

table2 <-  stor %>% tibble(
    Region = names(.),
    untidied = .
    ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) 

table2

storage <- list()
for(i in names(ThalPC)[-c(1:8)]){
  storage[[i]] <- lm(get(i) ~ Status, ThalPC)
}

n <- names(ThalPC)[-c(1:9)]

storage <- list()
for(i in seq_along(n)) {
  storage[[i]] <- coh_d(ThalPC, i ~ Status, se = TRUE)
}

a <- coh_d(ThalPC, Left_LGN ~ Status, se= TRUE)

a

table_one <- tableby(Status ~ ., data= ThalPC)
tab2 <- summary(table_one, title= "test", text= TRUE, results= "asis")

try <- effectsize(stor[[i]])

library(esvis)

coh_d(ThalPC, get(i) ~ Status, se = TRUE)


View(table2)

l1 <- lm(data= ThalPC, Right_CeM~ Status)

summary(l1)

effectsize(l1)
```
